---
title: "TBSignatureProfiler on Malnutrition Data"
author: "Evan Johnson"
date: "8/21/2020"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: "flatly"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages({
  library(SummarizedExperiment)
  library(SingleCellExperiment)
  library(tidyverse)
  library(TBSignatureProfiler)
  library(sva)
  library(Rtsne)
  library(umap)
  library(limma)
  library(DT)
  library(ComplexHeatmap)
  library(enrichR)
  library(singleCellTK)
})

```

## Make and combine new data 
```{r, eval=F}
india44 <- read.table("features_combined_44.txt", sep = "\t")
india48 <- read.table("features_combined_48.txt", sep = "\t")
coldata <- read.table("india_colData.txt", sep = "\t", header = TRUE)
rowdata <- read.table("feature_types.txt", header=TRUE)
  
#replace colnames of india44
colnames(india44) <- gsub(x = colnames(india44), pattern= "SO_5007_([A-B])[0-9,A-Z]_([0-9]*)_[1-2]", replace="102\\2\\1")

colnames(india44) <- gsub(x = colnames(india44), pattern= "SO_5007_Set2_102_0?([0-9][0-9][0-9][0-9][0-9])", replace="102\\1A")

# Check that gsub did not create two columns with same name
stopifnot(length(unique(colnames(india44)))==44)
# Check that all column names are present in coldata
stopifnot(all(colnames(india44) %in% coldata$SUBJID))

# india48 colname replace
colnames(india48) <- gsub(x=colnames(india48), pattern="X102.([0-9]*).([A-B])0?", replace="102\\1\\2")

# Check that gsub did not create two columns with same name
stopifnot(length(unique(colnames(india48)))==48)
# Check that all column names are present in coldata
stopifnot(all(colnames(india48) %in% coldata$SUBJID))

#combine the india files, match colData and rowData
india <- as.matrix(cbind(india44, india48))
india <- india[,match(coldata$SUBJID,colnames(india))]
rowdata <- rowdata[match(rownames(india),rowdata[,1]),]

# make Summarized Experiment object
indata <- SummarizedExperiment(assays = SimpleList(counts = as.matrix(india)), colData = coldata, rowData = rowdata)

saveRDS(indata, file = "indata_SCE.rds")
```

## Preprocess
```{r, eval=F}
# Want to have 10% present rate
#indata <- indata[apply(assay(indata,"counts") != 0, 1, mean)>.1,] 

## Correct some errors in metadata
colData(indata)$Tb_status[grep("074", colnames(indata))] <- "LTBI"
colData(indata)$Tb_status[grep("082", colnames(indata))] <- "LTBI"
colData(indata)$Tb_status[grep("111", colnames(indata))] <- "LTBI"

## Make Severely Malnourished column data
colData(indata)$Tb_status <- factor(gsub("activeTB", "TB", as.character(colData(indata)$Tb_status)))
colData(indata)$bmi_cat2 <- factor(gsub("severely malnourished", "mal", gsub("well nourished", "well", colData(indata)$bmi_cat2)))
colData(indata)$status <- factor(paste(colData(indata)$Tb_status, colData(indata)$bmi_cat2, sep="_"))
table(colData(indata)$status)

## Removing Outliers
indata <- indata[,-which(colnames(indata) %in% c("10200459B","10200335A","10200332A"))]

```



## Batch correct and make log_cpm
```{r, eval=F}
## Make batch variable
batch=rep(1,ncol(indata))
batch[colnames(indata) %in% c("10200247B")]=1
batch[colnames(indata) %in% c("10200227B","10200346A","10200381A","10200308A","10200361A","10200365B","10200467B","10200341A","10200374A", "10200548B","10200343A","10200374B","10200346A","10200377A") ]=1
batch[colnames(indata)%in% c("10200070A", "10200128A","10200056A", "10200075A","10200136A", "10200105A","10200034A","10200058A", "10200007A", "10200064A","10200159A","10200077A","10200073A","10200130A","10200181A","10200059A","10200040B","10200018B","10200065B","10200003B","10200024B","10200004B","10200009B","10200001B","10200057B","10200029B","10200077B","10200035B","10200061B","10200030B","10200063B","10200034B","10200010A","10200288A","10200082A","10200074A","10200060A","10200023A","10200140A","10200111A","10200112A","10200016A","10200015A","10200087A")]=2
colData(indata)$batch <- factor(batch)
rm(batch)

modcombat <- model.matrix(~colData(indata)$bmi_cat2+colData(indata)$Tb_status)

assay(indata, "combatseq") <- ComBat_seq(assay(indata, "counts"),
                                      colData(indata)$batch, group=NULL,
                                      covar_mod=modcombat)

indata <- mkAssay(indata, input_name = "combatseq", log=T)
saveRDS(indata, file = "indata_SCE_batchcorrect.rds")
```

## Load Data

```{r load}

indata <- readRDS("indata_SCE_batchcorrect.rds")
dim(indata)

## Filter to have 10% present rate
indata <- indata[apply(assay(indata,"counts") != 0, 1, mean)>.20,] 
dim(indata)

### Malnutrition only
indata <- indata[,which(colData(indata)$bmi_cat2 == "mal")]
dim(indata)

```

## Dimension reduction plots {.tabset}

### PCA {.tabset}

#### Before Batch Correction (color by Batch)
```{r}
indataTMP <- indata 
indataTMP <- mkAssay(indataTMP, input_name = "counts", log=T)

indataSCE <- SingleCellExperiment(assays = list(log_cpm = assay(indataTMP, "log_cpm")), colData = colData(indata))
colnames(indataSCE) <- colnames(indataTMP)
dim(indataSCE)

singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, colorBy = "batch",shape = "status")

  png(filename = "figures/PCA_raw.png", width = 4, height = 3, units = "in",
      res = 150)
singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, colorBy = "batch",shape = "status")
  dev.off()

rm(indataSCE)
rm(indataTMP)
```

#### After Batch Correction (color by Batch)
```{r}
indataSCE <- SingleCellExperiment(assays = list(log_cpm = assay(indata, "log_cpm")), colData = colData(indata))
colnames(indataSCE) <- colnames(indata)
dim(indataSCE)

singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, colorBy = "batch",shape = "status")

 png(filename = "figures/PCA_adj_colbatch.png", width = 4, height = 3, units = "in",
      res = 150)
singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, colorBy = "batch",shape = "status")
  dev.off()
  
rm(indataSCE)
```


#### After Batch Correction (color by TBstatus)
```{r}
indataSCE <- SingleCellExperiment(assays = list(log_cpm = assay(indata, "log_cpm")), colData = colData(indata))
colnames(indataSCE) <- colnames(indata)
dim(indataSCE)

singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, shape = "batch",colorBy = "status")

 png(filename = "figures/PCA_adj_colstatus.png", width = 4, height = 3, units = "in",
      res = 150)
singleCellTK::plotPCA(indataSCE, useAssay = "log_cpm", runPCA = TRUE, shape = "batch", colorBy = "status")
  dev.off()
  
rm(indataSCE)
```


### tSNE 
```{r}
set.seed(1)
tsne_out <- Rtsne(t(assay(indata,"log_cpm")), check_duplicates = FALSE, pca = TRUE, perplexity=10, theta=0.5, dims=2)

embedding <- as.data.frame(tsne_out$Y)
embedding$Class <- as.factor(indata$Tb_status)

g <- ggplot(embedding, aes(x=V1, y=V2, color=Class, label = colnames(assay(indata,"log_cpm")))) + geom_point(size=1.5) + xlab("T-SNE 1") + ylab("T-SNE 2") + theme(plot.title = element_text(hjust = 0.5)) + 
ggtitle("TSNE Plot")

plot(g)
```

### UMAP 
```{r}
set.seed(1)
umap_out <- umap(t(assay(indata,"log_cpm")))

embedding <- as.data.frame(umap_out$layout)
embedding$Class <- as.factor(indata$Tb_status)

g <- ggplot(embedding, aes(x=V1, y=V2, color=Class, label = colnames(assay(indata,"log_cpm")))) + geom_point(size=1.5) + xlab("UMAP 1") + ylab("UMAP 2") + theme(plot.title = element_text(hjust = 0.5)) + 
ggtitle("UMAP Plot")

plot(g)
```



## Differential Expression {.tabset}

### DE Genes
```{r}
designBC <- model.matrix(~Tb_status, data=colData(indata))
colnames(designBC) <- c("Intercept", "activeTB")
fitBC <- lmFit(assay(indata, "log_cpm"), designBC)

contrast.matrixTB<- makeContrasts(activeTB, levels = designBC)
fitTB <- contrasts.fit(fitBC,contrast.matrixTB)
fitTB <- eBayes(fitTB)
limmaResTB <- topTable(fitTB, adjust.method = "BH", n = Inf, sort.by = "P")

#Getting significant genes and rownames to plot
adjpcutoff <- 0.01
limmaResTB.sig <- subset(limmaResTB, adj.P.Val < adjpcutoff)
write.csv(limmaResTB.sig,"figures/malnut_only_siggenes.csv",quote=F)
datatable(limmaResTB.sig,options=list(scrollX=T,pageLength=15),rownames = T)

mean(unlist(TBsignatures) %in% rownames(limmaResTB.sig))

### keep only protein coding genes
annotations <- rowData(indata)[match(rownames(limmaResTB.sig), rowData(indata)[,1]),2]
table(annotations)

sigGenesTB <-rownames(limmaResTB.sig[annotations=="protein_coding",])

```

### Heatmap
```{r}

mat = as.matrix(assay(indata,"log_cpm")[sigGenesTB[1:500],])
mat = t(scale(t(mat)))

df=data.frame(TB_status=colData(indata)$Tb_status) 
ha = HeatmapAnnotation(df = df, col = list(TB_status=c("TB"="Red","LTBI"="Blue")))

Heatmap(mat,show_row_names=F,show_column_names = F, top_annotation = ha)
```

## Differential Expression Clustering Heatmap for the paper
```{r}
# some things related to colors
special_red <- RColorBrewer::brewer.pal(3, "Set1")[1]
special_blue <- RColorBrewer::brewer.pal(3, "Set1")[2]

# COLORS FOR HEATMAP
col.me <- viridis::viridis(15)
colorList <- list("status" = setNames(c("Red",
                                        "Blue"),
                                      c("TB_mal", "LTBI_mal")))

  mat <- as.matrix(assay(indata,"log_cpm")[sigGenesTB[1:500],])
  mat = t(scale(t(mat)))

  df <- data.frame("TB Status" = colData(indata)$Tb_status) 
  annot <- HeatmapAnnotation(df = df, col = list(TB.Status = c(
    "TB" = "Red", "LTBI" = "Blue")))
  
  png(filename = "figures/Heatmap_DIFF_EXP.png", width = 12, height = 10, units = "in",
      res = 150)
  Heatmap(mat, show_row_names = F,
          show_column_names = F,
          top_annotation = annot,
          col = col.me,
          name = "Expression")
  dev.off()
```
  
  
### Pathway analysis {.tabset}
```{r}
pathway=enrichr(sigGenesTB[1:1000],databases = c("WikiPathways_2013","Reactome_2016","KEGG_2016","Panther_2016"))
#pathway=enrichr(sigGenesTB,databases = c("WikiPathways_2013","Reactome_2016","KEGG_2016","Panther_2016"))
```

#### Wiki Pathways
```{r}
datatable(pathway$WikiPathways_2013[pathway$WikiPathways_2013$Adjusted.P.value<.5,],options=list(scrollX=T,pageLength=15),rownames = F)
```

#### Reactome Pathways
```{r}
datatable(pathway$Reactome_2016[pathway$Reactome_2016$Adjusted.P.value<.5,],options=list(scrollX=T,pageLength=15),rownames = F)
```

#### KEGG Pathways
```{r}
datatable(pathway$KEGG_2016[pathway$KEGG_2016$Adjusted.P.value<.5,],options=list(scrollX=T,pageLength=15),rownames = F)

```

#### Panther Pathways
```{r}
datatable(pathway$Panther_2016[pathway$Panther_2016$Adjusted.P.value<.5,],options=list(scrollX=T,pageLength=15),rownames = F)
```


## Run the TBSignatureProfiler

```{r}
TBsignatures$'Suliman_RISK_4' <- c("GAS6","SEPTIN4","CD1C","BLK")
TBsignatures$'Lee_4' <- c("INTS13", "DHX29", "NEMF",  "PTPRC")

indata$TB.status <- factor(paste(indata$status))
siglist_mal <- names(TBsignatures)

ssgsea_res <- runTBsigProfiler(indata, useAssay = "log_cpm", 
                               algorithm = "ssGSEA")
gsva_res <- runTBsigProfiler(indata, useAssay = "log_cpm", 
                               algorithm = "GSVA")
plage_res <- runTBsigProfiler(indata, useAssay = "log_cpm", 
                             algorithm = "PLAGE")

```


## Methods Figure 1: Overlap of genes in the TB signature cohort listed in 5 or more signatures
```{r}
# some things related to colors
special_red <- RColorBrewer::brewer.pal(3, "Set1")[1]
special_blue <- RColorBrewer::brewer.pal(3, "Set1")[2]

# COLORS FOR HEATMAP
col.me <- viridis::viridis(15)
colorList <- list("status" = setNames(c(special_red,
                                        special_blue),
                                      c("TB_mal", "LTBI_mal")))

png(filename = "figures/genes_in_5plus.png", width = 8, height = 7, 
      units = "in", res = 150)
  genesin5ormore <- names(sort(table(unlist(TBsignatures)), 
                               decreasing = TRUE)[sort(table(unlist(TBsignatures)),
                                                       decreasing = TRUE) > 4])
  geneoverlapdf <- data.frame(row.names = genesin5ormore)
  for(i in names(TBsignatures)){
    geneoverlapdf[,i] <- ifelse(rownames(geneoverlapdf)%in% TBsignatures[[i]], 
                                "Yes", "No")
  }
  geneoverlapdf <- geneoverlapdf[,order(colSums(geneoverlapdf == "Yes"), 
                                        decreasing = TRUE)]
  geneoverlapdf <- geneoverlapdf[order(rowSums(geneoverlapdf == "Yes"), 
                                       decreasing = TRUE),]
  draw(Heatmap(t(as.matrix(geneoverlapdf)), col = c("white", special_blue), 
               row_names_gp = gpar(fontsize = 8), 
               column_names_gp = gpar(fontsize = 8), 
               rect_gp = gpar(col="grey", lty = 1),
               name = "Gene in Signature"), 
       heatmap_legend_side = "bottom")
  dev.off()
```

## Methods Table 3: Percentage of overlapping genes between the TB signatures
```{r}  
overlap_matrix <- matrix(0, nrow = length(TBsignatures), 
                           ncol = length(TBsignatures))
  
  for (i in 1:length(TBsignatures)){
    for (j in 1:length(TBsignatures)){
      overlap_matrix[i, j] <- sum(
        !is.na(match(TBsignatures[[i]],
                     TBsignatures[[j]]))) / length(TBsignatures[[i]])
    }
  }
  
  rownames(overlap_matrix) <- colnames(overlap_matrix) <- names(TBsignatures)
  over_pct <- round(overlap_matrix, 3) * 100
  write.csv(overlap_matrix, file = "figures/overlap.csv", quote = FALSE)
  # Altered to add color afterward and saved as xslx workbook
```


## Figure 2. Heatmap of all signatures (ssGSEA)

```{r}
  png(filename = "figures/Heatmap_ssGSEA.png", width = 12, height = 10, units = "in",
      res = 150)
  signatureHeatmap(ssgsea_res, name = "ssGSEA", 
                   signatureColNames = names(TBsignatures),
                   annotationColNames = c("status"),
                   showColumnNames = FALSE, scale = TRUE,
                   choose_color = col.me,
                   cluster_columns = TRUE,
                   split_heatmap = "disease",
                   colList = colorList)
  dev.off()
```

## Supplementary Figure. Heatmap of all signatures  (GSVA)

```{r}
  png(filename = "figures/Heatmap_GSVA.png", width = 12, height = 10, units = "in",res = 150)
  signatureHeatmap(gsva_res, name = "GSVA", 
                   signatureColNames = names(TBsignatures),
                   annotationColNames = c("status"),
                   showColumnNames = FALSE, scale = TRUE,
                   choose_color = col.me,
                   cluster_columns = TRUE,
                   split_heatmap = "disease",
                   colList = colorList)
  dev.off()
```

## Figure 3a. Boxplots of AUCs (ssGSEA).

```{r}
  png(filename = "figures/AUC_boxplot_ssGSEA.png", width = 10, height = 10, 
      units = "in", res = 150)
  signatureBoxplot(ssgsea_res, name="ssGSEA", 
                   signatureColNames = names(TBsignatures),
                   annotationColName = c("status"), 
                   fill_colors = c(special_blue, special_red))
  dev.off()
```


## Figure 3b. Boxplot of the scores (LTBI vs. TB) by signature (ssGSEA).

```{r}
  png(filename = "figures/score_boxplot_ssGSEA.png", width = 7, height = 5, 
      units = "in", res = 150)
  par(mar = c(7,2,2,1))
  compareBoxplots(ssgsea_res, signatureColNames = names(TBsignatures),
                  annotationColName = "status", pb.show = TRUE,
                  name = "ssGSEA", rotateLabels = TRUE,
                  fill.col = special_red)
  dev.off()
```

## Supplementary Figure: Boxplots of AUCs (GSVA).
  
```{r}
  png(filename = "figures/AUC_boxplot_GSVA.png", width = 10, height = 10, units = "in",
      res = 150)
  signatureBoxplot(gsva_res, signatureColNames = names(TBsignatures),
                   annotationColName = c("status"), name = "GSVA",
                   fill_colors = c(special_blue, special_red), 
                   rotateLabels = TRUE)
  dev.off()
```

  
## Supplementary Figure: Boxplot of the scores (LTBI vs. TB) by signature (GSVA)

```{r}
  png(filename = "figures/score_boxplot_GSVA.png", width = 7, height = 5, 
      units = "in", res = 150)
  par(mar = c(7,2,2,1))
  compareBoxplots(gsva_res, signatureColNames = names(TBsignatures),
                  annotationColName = "status", pb.show = TRUE,
                  name = "GSVA", fill.col = special_red,
                  rotateLabels = TRUE)
  dev.off()
```

  
## Figure 4. Heatmap of genes for selected signatures {.tabset}
```{r}
  # Sambarey_HIV_10
  png(filename = "figures/Sambarey_HIV_10.png", width = 6, height = 4, units = "in",
      res = 150)
  signatureGeneHeatmap(ssgsea_res, useAssay = "log_cpm", 
                       sigGenes = TBsignatures[["Sambarey_HIV_10"]],
                       name = "Sambarey_HIV_10", signatureColNames = NULL, 
                       annotationColNames = c("status"), scale = TRUE,
                       choose_color = col.me,
                       colList = colorList,
                       cluster_columns = TRUE,
                       showColumnNames = FALSE)
  dev.off()
```

  
### Thompson_9
```{r}
  png(filename = "figures/Thompson_9.png", width = 6, height = 4, units = "in",
      res = 150)
  signatureGeneHeatmap(ssgsea_res, useAssay = "log_cpm", 
                       TBsignatures[["Thompson_9"]],
                       name = "Thompson_9", signatureColNames = NULL, 
                       choose_color = col.me,
                       colList = colorList,
                       annotationColNames = c("status"),
                       cluster_columns = TRUE,
                       showColumnNames = FALSE)
  dev.off()
```

  
### Lee_4
```{r}
  png(filename = "figures/Lee_4.png", width = 6, height = 4, units = "in",
      res = 150)
  signatureGeneHeatmap(ssgsea_res, useAssay = "log_cpm", 
                       TBsignatures[["Lee_4"]],
                       name = "Lee_4", signatureColNames = NULL, 
                       choose_color = col.me,
                       colList = colorList,
                       annotationColNames = c("status"),
                       cluster_columns = TRUE,
                       showColumnNames = FALSE)
  dev.off()
```

  
### Maertzdorf_4
```{r}
  png(filename = "figures/Maertzdorf_4.png", width = 6, height = 4, units = "in",
      res = 150)
  signatureGeneHeatmap(ssgsea_res, useAssay = "log_cpm", 
                       TBsignatures[["Maertzdorf_4"]],
                       name = "Maertzdorf_4", signatureColNames = NULL, 
                       choose_color = col.me,
                       colList = colorList,
                       annotationColNames = c("status"),
                       cluster_columns = TRUE,
                       showColumnNames = FALSE)
  dev.off()
```

  
## Supplementary figure: ROC curves for all signatures (ssGSEA).
```{r}
  # ssGSEA
  png(filename = "figures/ssgsea_ROC.png", width = 11, height = 9, units = "in",
      res = 150)
  signatureROCplot_CI(ssgsea_res, signatureColNames = names(TBsignatures),
                      scale = TRUE, annotationColName = "status",
                      name = 
                        "ROC Plots for Gene Signatures, 95% Confidence, ssGSEA",
                      nrow = 7, ncol = 7, choose_colors = c(special_blue,
                                                            "gray50",
                                                            "gray79"))
  dev.off()
  
```

  
## Supplementary figure: ROC curves for all signatures (GSVA).
```{r}
  png(filename = "figures/gsva_ROC.png", width = 11, height = 9, units = "in",
      res = 150)
  signatureROCplot_CI(gsva_res, signatureColNames = names(TBsignatures),
                      scale = TRUE, annotationColName = "status",
                      name = 
                        "ROC Plots for Gene Signatures, 95% Confidence, GSVA",
                      nrow = 7, ncol = 7, choose_colors = c(special_blue,
                                                            "gray50",
                                                            "gray79"),
                      )
  dev.off()
```
  
## Supplementary Table: TableAUC for ssGSEA 
```{r}
  out.ssgsea <- tableAUC(ssgsea_res, "status", names(TBsignatures),
                         output = "data.frame")

  # Add columns with t-test approach
  SE_scored <- ssgsea_res
  annotationColName <- "status"
  signatureColNames <- names(TBsignatures)
  annotationData <- droplevels(SummarizedExperiment::colData(
    SE_scored)[annotationColName][, 1])
  
  for (i in signatureColNames) {
    which.sig <- which(signatureColNames == i)
    score <- SummarizedExperiment::colData(SE_scored)[i][, 1]
    roc1 <- suppressMessages(pROC::roc(predictor = score,
                                       response = annotationData))
    conf <- pROC::ci.auc(roc1, method = "delong", progress = "none")
    out.ssgsea[which.sig, 7] <- conf[1]
    out.ssgsea[which.sig, 8] <- conf[2]
  }
  
  colnames(out.ssgsea)[c(7, 8)] <- c("LowerCISunXu", "UpperCISunXu")

  datatable(out.ssgsea)
  write.csv(out.ssgsea, file = "figures/ssGSEA_TableAUC.csv")
```
  
## Supplementary Table: TableAUC for GSVA 
```{r}
  out.gsva <- tableAUC(gsva_res, "status", names(TBsignatures), output = "data.frame")

  # Replace columns with t-test approach
  SE_scored <- gsva_res
  annotationColName <- "status"
  signatureColNames <- names(TBsignatures)
  annotationData <- droplevels(SummarizedExperiment::colData(
    SE_scored)[annotationColName][, 1])
  
  for (i in signatureColNames) {
    which.sig <- which(signatureColNames == i)
    score <- SummarizedExperiment::colData(SE_scored)[i][, 1]
    roc1 <- suppressMessages(pROC::roc(predictor = score,
                                       response = annotationData))
    conf <- pROC::ci.auc(roc1, method = "delong", progress = "none")
    out.gsva[which.sig, 7] <- conf[1]
    out.gsva[which.sig, 8] <- conf[2]
  }
  
  colnames(out.gsva)[c(7, 8)] <- c("LowerCISunXu", "UpperCISunXu")
  datatable(out.gsva)
```
  
## Supplementary Table: TableAUC for PLAGE 
```{r}
  out.plage <- tableAUC(plage_res, "status", names(TBsignatures),
                        output = "data.frame")

  # Replace columns with t-test approach
  SE_scored <- plage_res
  annotationColName <- "status"
  signatureColNames <- names(TBsignatures)
  annotationData <- droplevels(SummarizedExperiment::colData(
    SE_scored)[annotationColName][, 1])
  
  for (i in signatureColNames) {
    which.sig <- which(signatureColNames == i)
    score <- SummarizedExperiment::colData(SE_scored)[i][, 1]
    roc1 <- suppressMessages(pROC::roc(predictor = score,
                                       response = annotationData))
    conf <- pROC::ci.auc(roc1, method = "delong", progress = "none")
    out.plage[which.sig, 7] <- conf[1]
    out.plage[which.sig, 8] <- conf[2]
  }
  
  colnames(out.plage)[c(7, 8)] <- c("LowerCISunXu", "UpperCISunXu")

  datatable(out.plage)
```

## Supplementary Figure: Boxplots of AUCs (PLAGE).
```{r}
  png(filename = "figures/AUC_boxplot_PLAGE.png", width = 10, height = 10,
      units = "in",
      res = 150)
  signatureBoxplot(plage_res, signatureColNames = names(TBsignatures),
                   annotationColName = c("status"), name = "PLAGE",
                   fill_colors = c(special_blue, special_red), 
                   rotateLabels = TRUE)
  dev.off()
```
  
## Supplementary Figure: Boxplot of the scores (LTBI vs. TB) by signature (PLAGE)
```{r}
  png(filename = "figures/score_boxplot_PLAGE.png", width = 7, height = 5, 
      units = "in", res = 150)
  par(mar = c(7,2,2,1))
  compareBoxplots(plage_res, signatureColNames = names(TBsignatures),
                  annotationColName = "status", pb.show = TRUE,
                  name = "PLAGE", fill.col = special_red,
                  rotateLabels = TRUE)
  dev.off()
```
  
## Supplementary Figure: Heatmap of all signatures (PLAGE)
```{r}
  png(filename = "figures/Heatmap_PLAGE.png", width = 12, height = 10, units = "in",
      res = 150)
  signatureHeatmap(plage_res, name = "PLAGE", 
                   signatureColNames = names(TBsignatures),
                   annotationColNames = c("status"),
                   showColumnNames = FALSE, scale = TRUE,
                   choose_color = col.me,
                   cluster_columns = TRUE,
                   split_heatmap = "disease",
                   colList = colorList)
  dev.off()
```
  

##  Session Info
```{r session info}
sessionInfo()
```

